---
title: "PriorBeliefs_Figures"
author: "Hélène Van Marcke"
date: "9-1-2023"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r Preparation}
curdir <- dirname(rstudioapi::getSourceEditorContext()$path)
setwd(curdir)
library(reshape) #cast
library(timeSeries) #colSds
library(ggplot2)
library(Rmisc)
library(ggpubr)
library(ggplotify)

setwd("Data/Aggregated")
Data1 <- read.csv('data_exp1.csv')
Data2 <- read.csv('data_exp2.csv')
Simuls <- read.csv("model_prediction_exp1.csv")
Simuls2 <- read.csv("model_prediction_exp2.csv")
load("param_ddm_test_exp1.Rdata")
load("param_ddm_test_exp2.Rdata")
load("param_train_exp1.Rdata")
load("param_train_exp2.Rdata")
setwd(curdir)

subs1 <- sort(unique(Data1$sub))
Nsub_1 <- length(subs1) 
cond_1 <- sort(unique(Data1$fbcond))
Ncond <- length(cond_1)
trialdifflevel <- sort(unique(Data1$trialdifflevel))
Ndiff <- length(trialdifflevel)

subs_2 <- sort(unique(Data2$sub))
Nsub_2 <- length(subs_2)
cond_2 <- sort(unique(Data2$traindiffcond))
Ncond_2 <- length(cond_2)
trialdifflevel <- sort(unique(Data2$trialdifflevel))
Ndiff <- length(trialdifflevel)


# Functions and parameters ----

transp <- function(color, percent = 70, name = NULL) {
  rgb.val <- col2rgb(color)
  transp <- rgb(rgb.val[1], rgb.val[2], rgb.val[3],
                max = 255,
                alpha = (100 - percent) * 255 / 100,
                names = name)
    invisible(transp)
}

error.bar <- function(x, y, upper, lower=upper, length=0,...){
  if(length(x) != length(y) | length(y) !=length(lower) | length(lower) != length(upper))
    stop("vectors must be same length")
  arrows(x,y+upper, x, y-lower, angle=90, code=3, length=length, ...)
}


theme_set(theme_bw())
theme_update(panel.grid.major = element_line(colour = "white"),
             panel.grid.minor = element_line(colour = "white"),
             axis.title = element_text(colour = "grey30",size=13),
             axis.title.y = element_text(vjust = +3),
             axis.title.x = element_text(vjust = -0.75))

col_low="#CC6677"
col_av="#44AA99"
col_high="#E69F00"


```

# Figure 3

## Top panel

Objective performance: behavioural data and model fits for exp1 (A) and exp2 (B).

### Accuracy, exp 1 

```{r}

## Experiment 1
cor_sum = summarySE(Data1, measurevar = "cor", 
                         groupvars = c("trialdifflevel", "fbcond"))

# Simulated data
cor_sim <-  aggregate(.~sub+trialdifflevel+condition,Simuls,mean)
cor_simsum = summarySE(cor_sim, measurevar = "cor", 
                         groupvars = c("trialdifflevel", "condition"))

cor_sum$sim_ymin <- cor_simsum$cor-cor_simsum$se
cor_sum$sim_ymax <- cor_simsum$cor+cor_simsum$se



# PLOT
(acc_exp1 <- ggplot(data=cor_sum, 
             aes(y=cor, x=factor(trialdifflevel,level = c('hard','average','easy')),
                 color=factor(fbcond,level = c('lowSC','highSC','mediumSC')))) + 

  scale_color_manual(values = c(col_high,col_av,col_low),
                    labels=c('hard', 'average','easy')) +

  # Add modeling Data
  geom_ribbon(aes(ymin=sim_ymin, ymax=sim_ymax, 
                 group=fbcond,
                 fill=factor(fbcond,level = c('lowSC','highSC','mediumSC'))),
              colour="white",alpha=0.2) +
  
  # Add behavioural Data
  geom_point(size=1) +
  geom_line(aes(group=fbcond),size=.6)+
  geom_errorbar(aes(ymin=cor-se, ymax=cor+se), width=.04) +

  scale_y_continuous(limits = c(0.55, 1), expand = c(0.01,0.01)) +
  scale_x_discrete(labels=c("hard","average","easy"), expand = c(0.02,0.02)) +

  labs(title = "A.",
       x = "",
       y = "Accuracy") +
  theme(legend.position = "none",
        plot.title.position = "plot",
        plot.title = element_text(face = "bold"))
)


```

### RT, exp 1

```{r}

## Experiment 1
rt_sum = summarySE(Data1, measurevar = "rt", 
                         groupvars = c("trialdifflevel", "fbcond"))

# Simulated data
rt_sim <-  aggregate(.~sub+trialdifflevel+condition,Simuls,mean)
rt_simsum = summarySE(rt_sim, measurevar = "rt", 
                         groupvars = c("trialdifflevel", "condition"))

rt_sum$sim_ymin <- rt_simsum$rt-rt_simsum$se
rt_sum$sim_ymax <- rt_simsum$rt+rt_simsum$se



# PLOT
(rt_exp1 <- ggplot(data=rt_sum, 
             aes(y=rt, x=factor(trialdifflevel,level = c('hard','average','easy')),
                 color=factor(fbcond,level = c('lowSC','highSC','mediumSC')))) + 

  scale_color_manual(values = c(col_high,col_av,col_low),
                    labels=c('hard', 'average','easy')) +

  # Add modeling Data
  geom_ribbon(aes(ymin=sim_ymin, ymax=sim_ymax, 
                 group=fbcond,
                 fill=factor(fbcond,level = c('lowSC','highSC','mediumSC'))),
              colour="white",alpha=0.2) +
  
  # Add behavioural Data
  geom_point(size=1) +
  geom_line(aes(group=fbcond),size=.6)+
  geom_errorbar(aes(ymin=rt-se, ymax=rt+se), width=.04) +

  scale_y_continuous(limits = c(0.6, 1.1), expand = c(0.01,0.01)) +
  scale_x_discrete(labels=c("hard","average","easy"), expand = c(0.02,0.02)) +

  labs(title = "",
       x = "",
       y = "RT (s)") +
  theme(legend.position = "none",
        plot.title.position = "plot",
        plot.title = element_text(face = "bold"))
)

```



### Accuracy, exp 2

```{r}

## Experiment 1
cor_sum = summarySE(Data2, measurevar = "cor", 
                         groupvars = c("trialdifflevel", "traindiffcond"))

# Simulated data
cor_sim <-  aggregate(.~sub+trialdifflevel+condition,Simuls2,mean)
cor_simsum = summarySE(cor_sim, measurevar = "cor", 
                         groupvars = c("trialdifflevel", "condition"))

cor_sum$sim_ymin <- cor_simsum$cor-cor_simsum$se
cor_sum$sim_ymax <- cor_simsum$cor+cor_simsum$se



# PLOT
(acc_exp2 <- ggplot(data=cor_sum, 
             aes(y=cor, x=factor(trialdifflevel,level = c('hard','average','easy')),
                 color=factor(traindiffcond,level = c('hard','easy','average')))) + 

  scale_color_manual(values = c(col_high,col_av,col_low),
                    labels=c('hard', 'average','easy')) +

  # Add modeling Data
  geom_ribbon(aes(ymin=sim_ymin, ymax=sim_ymax, 
                 group=traindiffcond,
                 fill=factor(traindiffcond,level = c('hard','easy','average'))),
              colour="white",alpha=0.2) +
  
  # Add behavioural Data
  geom_point(size=1) +
  geom_line(aes(group=traindiffcond),size=.6)+
  geom_errorbar(aes(ymin=cor-se, ymax=cor+se), width=.04) +

  scale_y_continuous(limits = c(0.55, 1), expand = c(0.01,0.01)) +
  scale_x_discrete(labels=c("hard","average","easy"), expand = c(0.02,0.02)) +

  labs(title = "B.",
       x = "",
       y = "Accuracy") +
  theme(legend.position = "none",
        plot.title.position = "plot",
        plot.title = element_text(face = "bold"))
)


```

### RT, exp 2

```{r}

## Experiment 1
rt_sum = summarySE(Data2, measurevar = "rt", 
                         groupvars = c("trialdifflevel", "traindiffcond"))

# Simulated data
rt_sim <-  aggregate(.~sub+trialdifflevel+condition,Simuls2,mean)
rt_simsum = summarySE(rt_sim, measurevar = "rt", 
                         groupvars = c("trialdifflevel", "condition"))

rt_sum$sim_ymin <- rt_simsum$rt-rt_simsum$se
rt_sum$sim_ymax <- rt_simsum$rt+rt_simsum$se



# PLOT
(rt_exp2 <- ggplot(data=rt_sum, 
             aes(y=rt, x=factor(trialdifflevel,level = c('hard','average','easy')),
                 color=factor(traindiffcond,level = c('hard','easy','average')))) + 

  scale_color_manual(values = c(col_high,col_av,col_low),
                    labels=c('hard', 'average','easy')) +

  # Add modeling Data
  geom_ribbon(aes(ymin=sim_ymin, ymax=sim_ymax, 
                 group=traindiffcond,
                 fill=factor(traindiffcond,level = c('hard','easy','average'))),
              colour="white",alpha=0.2) +
  
  # Add behavioural Data
  geom_point(size=1) +
  geom_line(aes(group=traindiffcond),size=.6)+
  geom_errorbar(aes(ymin=rt-se, ymax=rt+se), width=.04) +

  scale_y_continuous(limits = c(0.6, 1.1), expand = c(0.01,0.01)) +
  scale_x_discrete(labels=c("hard","average","easy"), expand = c(0.02,0.02)) +

  labs(title = "",
       x = "",
       y = "RT (s)") +
  theme(legend.position = "none",
        plot.title.position = "plot",
        plot.title = element_text(face = "bold"))
)

```


## Middle panel

Confidence data (main results)

```{r}

## Experiment 1
cj_sum = summarySE(Data1, measurevar = "cj", 
                         groupvars = c("trialdifflevel", "fbcond"))

cj_sum_ind <- with(Data1,aggregate(cj,by=list(sub,fbcond,trialdifflevel),mean))
names(cj_sum_ind) <- c("sub","fbcond","trialdifflevel","cj")

cj_sum$fbcond <- factor(cj_sum$fbcond, levels = c("lowSC","mediumSC","highSC"))
cj_sum_ind$fbcond <- factor(cj_sum_ind$fbcond, levels = c("lowSC", "mediumSC", "highSC"))

levels(cj_sum$fbcond) <- c("negative", "average", "positive")
levels(cj_sum_ind$fbcond) <- c("negative", "average", "positive")

# PLOT
(cj_exp1 <- ggplot(data=cj_sum, 
             aes(y=cj, x=factor(trialdifflevel,level = c('hard','average','easy')),
                 color=factor(fbcond))) + 
  
  scale_color_manual(values = c(col_high,col_av,col_low),
                    labels=c('negative', 'average','positive')) +

  # Individual datapoints
  geom_point(data=cj_sum_ind, aes(y=cj,
                                  x=factor(trialdifflevel,level = c('hard','average','easy')),
                                  shape=factor(fbcond)),
            size=1.5,alpha=.35,
            position = position_jitterdodge(jitter.width=0.15,dodge.width = 0.3)) +

    
  # Add modeling Data
  geom_ribbon(aes(ymin=cj-se,ymax=cj+se,
                  group=fbcond,
                  fill=factor(fbcond)),
              colour="white",
              position=position_dodge(0.3),
              alpha=0.6) +
    
  scale_fill_manual(values = c(col_high,col_av,col_low),
                    labels=c('negative', 'average','positive')) +
    
  # Add summarised Data
  geom_point(size=2,aes(shape=fbcond),position=position_dodge(0.3)) +
     
 # geom_line(aes(group=fbcond),size=.6,position=position_dodge(0.3))+
    
 # geom_errorbar(aes(ymin=cj-se, ymax=cj+se), 
  #              width=.1,size=.8,position=position_dodge(0.3)) +

    
  scale_y_continuous(limits = c(3,6), expand = c(0.01,0.01)) +
  scale_x_discrete(labels=c('negative', 'average','positive'), expand = c(0.03,0.03)) +

  labs(title = "C.",
       x = "",
       y = "Confidence",
       fill="Exp. 1: Comparative feedback",
       color="Exp. 1: Comparative feedback",
       shape="Exp. 1: Comparative feedback") +
  theme(legend.position = "top",
        legend.title = element_text(face = "bold"),
        plot.title.position = "plot",
        plot.title = element_text(face = "bold"),
        axis.text = element_text(size = 12),
        axis.title = element_text(size = 12)) +
  
    guides(color = guide_legend(title.position="top", title.hjust = 0.5),
         fill = guide_legend(title.position="top", title.hjust = 0.5),
         shape = guide_legend(title.position="top", title.hjust = 0.5))
)


legend1 <- as.ggplot(get_legend(cj_exp1))


(cj_exp1 <- ggplot(data=cj_sum, 
             aes(y=cj, x=factor(trialdifflevel,level = c('hard','average','easy')),
                 color=factor(fbcond))) + 
  scale_color_manual(values = c(col_high,col_av,col_low),
                    labels=c('Negative', 'Average','Positive')) +
  geom_point(data=cj_sum_ind, aes(y=cj,
                                  x=factor(trialdifflevel,level = c('hard','average','easy')),
                                  shape=factor(fbcond)),
            size=1.5,alpha=.35,
            position = position_jitterdodge(jitter.width=0.15,dodge.width = 0.3)) +
  geom_ribbon(aes(ymin=cj-se,ymax=cj+se,
                  group=fbcond,
                  fill=factor(fbcond)),
              colour="white",
              position=position_dodge(0.3),
              alpha=0.6) +
    
  scale_fill_manual(values = c(col_high,col_av,col_low),
                    labels=c('Negative', 'Average','Positive')) +
  geom_point(size=2,aes(shape=fbcond),position=position_dodge(0.3)) +
  scale_y_continuous(limits = c(3,6), expand = c(0.01,0.01)) +
  scale_x_discrete(labels=c('Negative', 'Average','Positive'), expand = c(0.03,0.03)) +
  labs(title = "C.",
       x = "",
       y = "Confidence",
       fill="Exp. 1: Comparative feedback",
       color="Exp. 1: Comparative feedback",
       shape="Exp. 1: Comparative feedback") +
  theme(legend.position = "none",
        legend.title = element_text(face = "bold"),
        plot.title.position = "plot",
        plot.title = element_text(face = "bold"),
        axis.text = element_text(size = 12),
        axis.title = element_text(size = 12)) +
  guides(color = guide_legend(title.position="top", title.hjust = 0.5),
         fill = guide_legend(title.position="top", title.hjust = 0.5),
         shape = guide_legend(title.position="top", title.hjust = 0.5))
)

```



Exp 2

```{r}
Data2 <- subset(Data2,cor==0)
## Experiment 1
cj_sum = summarySE(Data2, measurevar = "cj", 
                         groupvars = c("trialdifflevel", "traindiffcond"))

cj_sum_ind <- with(Data2,aggregate(cj,by=list(sub,traindiffcond,trialdifflevel),mean))
names(cj_sum_ind) <- c("sub","traindiffcond","trialdifflevel","cj")

cj_sum$traindiffcond <- factor(cj_sum$traindiffcond, levels = c("hard", "average", "easy"))
cj_sum_ind$traindiffcond <- factor(cj_sum_ind$traindiffcond, levels = c("hard", "average", "easy"))


# PLOT
(cj_exp2 <- ggplot(data=cj_sum, 
             aes(y=cj, x=factor(trialdifflevel,level = c('hard','average','easy')),
                 color=factor(traindiffcond))) + 
  
  scale_color_manual(values = c(col_high,col_av,col_low),
                    labels=c('hard', 'average','easy')) +

  # Individual datapoints
  geom_point(data=cj_sum_ind, aes(y=cj,
                                  x=factor(trialdifflevel,level = c('hard','average','easy')),
                                  shape=factor(traindiffcond)),
            size=1.5,alpha=.35,
            position = position_jitterdodge(jitter.width=0.15,dodge.width = 0.3)) +

    
  # Add modeling Data
  geom_ribbon(aes(ymin=cj-se,ymax=cj+se,
                  group=traindiffcond,
                  fill=factor(traindiffcond)),
              colour="white",
              position=position_dodge(0.3),
              alpha=0.6) +
    
  scale_fill_manual(values = c(col_high,col_av,col_low),
                    labels=c('hard', 'average','easy')) +
    
  # Add summarised Data
  geom_point(size=2,aes(shape=traindiffcond),position=position_dodge(0.3)) +
     
 # geom_line(aes(group=traindiffcond),size=.6,position=position_dodge(0.3))+
    
 # geom_errorbar(aes(ymin=cj-se, ymax=cj+se), 
  #              width=.1,size=.8,position=position_dodge(0.3)) +

    
 # scale_y_continuous(limits = c(3,6), expand = c(0.01,0.01)) +
  scale_x_discrete(labels=c("hard","average","easy"), expand = c(0.03,0.03)) +

  
  labs(title = "D.",
       x = "",
       y = "",
       fill="Exp. 2: Training difficulty",
       color="Exp. 2: Training difficulty",
       shape="Exp. 2: Training difficulty") +
    
  theme(legend.position = "top",
        legend.title = element_text(face = "bold"),
        plot.title.position = "plot",
        plot.title = element_text(face = "bold"),
        axis.text = element_text(size = 12),
        axis.title = element_text(size = 12)) +
  
    guides(color = guide_legend(title.position="top", title.hjust = 0.5),
         fill = guide_legend(title.position="top", title.hjust = 0.5),
         shape = guide_legend(title.position="top", title.hjust = 0.5))
)


legend2 <- as.ggplot(get_legend(cj_exp2))



(cj_exp2 <- ggplot(data=cj_sum, 
             aes(y=cj, x=factor(trialdifflevel,level = c('hard','average','easy')),
                 color=factor(traindiffcond))) + 
  
  scale_color_manual(values = c(col_high,col_av,col_low),
                    labels=c('hard', 'average','easy')) +
  geom_point(data=cj_sum_ind, aes(y=cj,
                                  x=factor(trialdifflevel,level = c('hard','average','easy')),
                                  shape=factor(traindiffcond)),
            size=1.5,alpha=.35,
            position = position_jitterdodge(jitter.width=0.15,dodge.width = 0.3)) +
  geom_ribbon(aes(ymin=cj-se,ymax=cj+se,
                  group=traindiffcond,
                  fill=factor(traindiffcond)),
              colour="white",
              position=position_dodge(0.3),
              alpha=0.6) +
    
  scale_fill_manual(values = c(col_high,col_av,col_low),
                    labels=c('hard', 'average','easy')) +
  geom_point(size=2,aes(shape=traindiffcond),position=position_dodge(0.3)) +
  scale_y_continuous(limits = c(3,6), expand = c(0.01,0.01)) +
  scale_x_discrete(labels=c("hard","average","easy"), expand = c(0.03,0.03)) +
  labs(title = "D.",
       x = "",
       y = "",
       fill="Exp. 2: Training difficulty",
       color="Exp. 2: Training difficulty",
       shape="Exp. 2: Training difficulty") +
  theme(legend.position = "none",
        legend.title = element_text(face = "bold"),
        plot.title.position = "plot",
        plot.title = element_text(face = "bold"),
        axis.text = element_text(size = 12),
        axis.title = element_text(size = 12)) +
  guides(color = guide_legend(title.position="top", title.hjust = 0.5),
         fill = guide_legend(title.position="top", title.hjust = 0.5),
         shape = guide_legend(title.position="top", title.hjust = 0.5))
)

```


## Bottom panel

Qualitative modeling data 

```{r}

# Simulated data
cj_sim <-  aggregate(.~sub+trialdifflevel+condition,Simuls,mean)
cj_simsum = summarySE(cj_sim, measurevar = "cj", 
                         groupvars = c("trialdifflevel", "condition"))

cj_simsum$fbcond <- factor(cj_simsum$condition, levels = c("lowSC", "mediumSC", "highSC"))


# PLOT
(cj_sim_exp1 <- ggplot(data=cj_simsum, 
             aes(y=cj, x=factor(trialdifflevel,level = c('hard','average','easy')),
                 color=factor(fbcond))) + 
  
  scale_color_manual(values = c(col_high,col_av,col_low),
                    labels=c('hard', 'average','easy')) +
  
  # Add Data
  geom_ribbon(aes(ymin=cj-se,ymax=cj+se,
                  group=fbcond,
                  fill=factor(fbcond)),
              colour="white",
              alpha=0.6) +
    
  scale_fill_manual(values = c(col_high,col_av,col_low),
                    labels=c('hard', 'average','easy')) +
    
  # Add summarised Data
  geom_point(size=2,aes(shape=fbcond)) +
     
 # geom_line(aes(group=fbcond),size=.6,position=position_dodge(0.3))+
    
 # geom_errorbar(aes(ymin=cj-se, ymax=cj+se), 
  #              width=.1,size=.8,position=position_dodge(0.3)) +

    
  scale_y_continuous(limits = c(.5,.92), expand = c(0.01,0.01)) +
  scale_x_discrete(labels=c("hard","average","easy"), expand = c(0.03,0.03)) +

  labs(title = "E. Model predictions",
       x = "",
       y = "Confidence") +
  theme(legend.position = "none",
        plot.title.position = "plot",
        plot.title = element_text(face = "bold"),
        axis.text = element_text(size = 12),
        axis.title = element_text(size = 12))
)

```


Exp 2

```{r}

# Simulated data
cj_sim <-  aggregate(.~sub+trialdifflevel+condition,Simuls2,mean)
cj_simsum = summarySE(cj_sim, measurevar = "cj", 
                         groupvars = c("trialdifflevel", "condition"))

cj_simsum$fbcond <- factor(cj_simsum$condition, levels = c("hard", "average", "easy"))


# PLOT
(cj_sim_exp2 <- ggplot(data=cj_simsum, 
             aes(y=cj, x=factor(trialdifflevel,level = c('hard','average','easy')),
                 color=factor(fbcond))) + 
  
  scale_color_manual(values = c(col_high,col_av,col_low),
                    labels=c('hard', 'average','easy')) +
  
  # Add Data
  geom_ribbon(aes(ymin=cj-se,ymax=cj+se,
                  group=fbcond,
                  fill=factor(fbcond)),
              colour="white",
              alpha=0.6) +
    
  scale_fill_manual(values = c(col_high,col_av,col_low),
                    labels=c('hard', 'average','easy')) +
    
  # Add summarised Data
  geom_point(size=2,aes(shape=fbcond)) +
     
 # geom_line(aes(group=fbcond),size=.6,position=position_dodge(0.3))+
    
 # geom_errorbar(aes(ymin=cj-se, ymax=cj+se), 
  #              width=.1,size=.8,position=position_dodge(0.3)) +

    
  scale_y_continuous(limits = c(.5,.92), expand = c(0.01,0.01)) +
  scale_x_discrete(labels=c("hard","average","easy"), expand = c(0.03,0.03)) +

  labs(title = "",
       x = "",
       y = "") +
  theme(legend.position = "none",
        plot.title.position = "plot",
        plot.title = element_text(face = "bold"),
        axis.text = element_text(size = 12))
)

```


```{r}

library(grid)
library(gridExtra)

jpeg(
  filename="MainFigure.jpeg",
  width=10,
  height=13,
  units="in",
  res=500)

lay <- rbind(c(0,0,1,1),
             c(2,3,4,5),
             c(6,6,7,7),
             c(6,6,7,7),
             c(8,8,9,9),
             c(8,8,9,9))

grid.arrange(legend1,legend2,
             acc_exp1,rt_exp1,acc_exp2,rt_exp2,
             cj_exp1,cj_exp2,
             cj_sim_exp1,cj_sim_exp2,
             layout_matrix=lay)


dev.off()


```



# Figure 4

## Exp 1

```{r}

# Subjective drift 

plot_vs <- with(param_train_exp1,aggregate(Vs,by=list(sub,condition),mean))
names(plot_vs) <- c("sub","cond","vs")


plot_vs$cond <- factor(plot_vs$cond,levels=c("lowSC","mediumSC","highSC"))
levels(plot_vs$cond) <- c("negative", "average", "positive")

# sort by subject or the jitter doesn't align between points and lines - even with seed
# see https://github.com/tidyverse/ggplot2/issues/3535 
# OR next time, switch condition and sub arguments above :)
plot_vs <-
  plot_vs %>%
  arrange(sub, cond)


# PLOT
(vs_exp1 <- ggplot(data=plot_vs, aes(y=vs, x=cond)) + 
  
  geom_line(aes(group=sub),size=.5,col="grey",alpha=.5,
             position = position_jitter(0.05, seed=2))+
  geom_point(size=2,col="grey",alpha=.6,
             position = position_jitter(0.05,seed=2)) +
  
  stat_summary(aes(group=1),geom = "line",fun = "mean",col = "black",size = 1.5) +
  stat_summary(geom = "point",fun = "mean",col = "black",size = 3) +
  stat_summary(fun.data = mean_se,geom = "errorbar",width=0,size=1) + 
    
  scale_y_continuous(expand = c(0.01,0.01)) +
  scale_x_discrete(labels=c("Negative","Average","Positive"), expand = c(0.04,0.04)) +

  labs(title = "A.",
       x = "",
       y = "Subjective drift") +
  theme(legend.position = "none",
        plot.title.position = "plot",
        plot.title = element_text(face = "bold"),
        axis.text = element_text(size = 12),
        plot.margin = margin(.7,.7,0,.7, "cm"))

)


```


```{r}

## Non-decision time

plot_ter <- with(param_ddm_test_exp1,aggregate(ter,by=list(condition,sub),mean))
names(plot_ter) <- c("cond","sub","ter")

plot_ter$cond <- factor(plot_ter$cond,levels=c("lowSC","mediumSC","highSC"))
levels(plot_ter$cond) <- c("negative", "average", "positive")

plot_ter <-
  plot_ter %>%
  arrange(sub, cond)


# PLOT
(ter_exp1 <- ggplot(data=plot_ter, aes(y=ter, x=cond)) + 
  
  geom_line(aes(group=sub),size=.5,col="grey",alpha=.5,
             position = position_jitter(0.05, seed=2))+
  geom_point(size=2,col="grey",alpha=.6,
             position = position_jitter(0.05,seed=2)) +
  
  stat_summary(aes(group=1),geom = "line",fun = "mean",col = "black",size = 1.5) +
  stat_summary(geom = "point",fun = "mean",col = "black",size = 3) +
  stat_summary(fun.data = mean_se,geom = "errorbar",width=0,size=1) + 
    
  scale_y_continuous(expand = c(0.01,0.01)) +
  scale_x_discrete(labels=c("Negative","Average","Positive"), expand = c(0.04,0.04)) +

  labs(title = "C.",
       x = "Feedback condition",
       y = "Non-decision time") +
  theme(legend.position = "none",
        plot.title.position = "plot",
        plot.title = element_text(face = "bold"),
        axis.text = element_text(size = 12),
        axis.title = element_text(size = 13),
        plot.margin = margin(.5,.7,.7,.7, "cm"))

)

```

```{r}

## Bound

plot_bound <- with(param_ddm_test_exp1,aggregate(bound,by=list(condition,sub),mean))
names(plot_bound) <- c("cond","sub","bound")

plot_bound$cond <- factor(plot_bound$cond,levels=c("lowSC","mediumSC","highSC"))
levels(plot_bound$cond) <- c("negative", "average", "positive")

plot_bound <-
  plot_bound %>%
  arrange(sub, cond)


# PLOT
(bound_exp1 <- ggplot(data=plot_bound, aes(y=bound, x=cond)) + 
  
  geom_line(aes(group=sub),size=.5,col="grey",alpha=.5,
             position = position_jitter(0.05, seed=2))+
  geom_point(size=2,col="grey",alpha=.6,
             position = position_jitter(0.05,seed=2)) +
  
  stat_summary(aes(group=1),geom = "line",fun = "mean",col = "black",size = 1.5) +
  stat_summary(geom = "point",fun = "mean",col = "black",size = 3) +
  stat_summary(fun.data = mean_se,geom = "errorbar",width=0,size=1) + 
    
  scale_y_continuous(expand = c(0.01,0.01)) +
  scale_x_discrete(labels=c("Negative","Average","Positive"), expand = c(0.04,0.04)) +

  labs(title = "D.",
       x = "Feedback condition",
       y = "Bound") +
  theme(legend.position = "none",
        plot.title.position = "plot",
        plot.title = element_text(face = "bold"),
        axis.text = element_text(size = 12),
        plot.margin = margin(.5,.7,.7,.7, "cm"))

)

```

```{r}

## Drift interaction

plot_drift <- with(param_ddm_test_exp1,aggregate(drift,by=list(sub,condition,difflevel),mean))
names(plot_drift) <- c("sub","cond","trialdiff","drift")

plot_drift$cond <- factor(plot_drift$cond,levels=c("lowSC","mediumSC","highSC"))
levels(plot_drift$cond) <- c("negative", "average", "positive")

plot_drift$trialdiff <- factor(plot_drift$trialdiff,levels=c("easy","average","hard"))
levels(plot_drift$trialdiff) <- c("Easy", "Average", "Hard")

plot_drift = summarySE(plot_drift, measurevar = "drift", 
                         groupvars = c("trialdiff", "cond"))

# PLOT
(drift_exp1 <- ggplot(data=plot_drift, aes(y=drift,x=cond,col=trialdiff)) + 
  
  geom_line(aes(group=trialdiff,linetype=trialdiff),size=1)+
  geom_point(size=2) +
  geom_errorbar(aes(ymin=drift-se, ymax=drift+se),width=0,size=.8) +
    
  scale_color_manual(values=c('orange', 'darkorange3','orangered4')) +

  scale_y_continuous(limits=c(0,.25),expand = c(0.01,0.01)) +
  scale_x_discrete(labels=c("Negative","Average","Positive"), expand = c(0.04,0.04)) +

  labs(title = "B.",
       x = "",
       y = "Drift rate",
       color= "Trial difficulty:",
       linetype= "Trial difficulty:") +
    
  theme(legend.position = c(.5,.1),
        plot.title.position = "plot",legend.direction="horizontal",
        plot.title = element_text(face = "bold"),
        axis.text = element_text(size = 12),
        legend.title = element_text(size=10),
        plot.margin = margin(.7,.7,0,.7, "cm")) 
  #guides(color = guide_legend(title.position="top", title.hjust = 0.5))

)


```


```{r}

library(grid)
library(gridExtra)

jpeg(
  filename="ModelParameters_Exp1.jpeg",
  width=10,
  height=7,
  units="in",
  res=500)

lay <- rbind(c(1,2),
             c(3,4))

grid.arrange(vs_exp1,drift_exp1,ter_exp1,bound_exp1,
             layout_matrix=lay,
             top=textGrob("Exp. 1: Comparative feedback",gp=gpar(fontsize=13,font=2)))


dev.off()


```


## Exp 2

```{r}

# Subjective drift 
plot_vs <- with(param_train_exp2,aggregate(Vs,by=list(condition,sub),mean))
names(plot_vs) <- c("cond","sub","vs")

plot_vs$cond <- factor(plot_vs$cond,levels=c("hard","average","easy"))
levels(plot_vs$cond)

plot_vs <-
  plot_vs %>%
  arrange(sub, cond)

# PLOT
(vs_exp2 <- ggplot(data=plot_vs, aes(y=vs, x=cond)) + 
  
  geom_line(aes(group=sub),size=.5,col="grey",alpha=.5,
             position = position_jitter(0.05, seed=2))+
  geom_point(size=2,col="grey",alpha=.6,
             position = position_jitter(0.05,seed=2)) +
  
  stat_summary(aes(group=1),geom = "line",fun = "mean",col = "black",size = 1.5) +
  stat_summary(geom = "point",fun = "mean",col = "black",size = 3) +
  stat_summary(fun.data = mean_se,geom = "errorbar",width=0,size=1) + 
    
  scale_y_continuous(expand = c(0.01,0.01)) +
  scale_x_discrete(labels=c("hard","average","easy"), expand = c(0.04,0.04)) +

  labs(title = "E.",
       x = "",
       y = "Subjective drift") +
  theme(legend.position = "none",
        plot.title.position = "plot",
        plot.title = element_text(face = "bold"),
        axis.text = element_text(size = 12),
        plot.margin = margin(.7,.7,0,.7, "cm"))

)


```


```{r}

## Non-decision time

plot_ter <- with(param_ddm_test_exp2,aggregate(ter,by=list(condition,sub),mean))
names(plot_ter) <- c("cond","sub","ter")

plot_ter$cond <- factor(plot_ter$cond,levels=c("hard","average","easy"))
levels(plot_ter$cond)

plot_ter <-
  plot_ter %>%
  arrange(sub, cond)


# PLOT
(ter_exp2 <- ggplot(data=plot_ter, aes(y=ter, x=cond)) + 
  
  geom_line(aes(group=sub),size=.5,col="grey",alpha=.5,
             position = position_jitter(0.05, seed=2))+
  geom_point(size=2,col="grey",alpha=.6,
             position = position_jitter(0.05,seed=2)) +
  
  stat_summary(aes(group=1),geom = "line",fun = "mean",col = "black",size = 1.5) +
  stat_summary(geom = "point",fun = "mean",col = "black",size = 3) +
  stat_summary(fun.data = mean_se,geom = "errorbar",width=0,size=1) + 
    
  scale_y_continuous(expand = c(0.01,0.01)) +
  scale_x_discrete(labels=c("hard","average","easy"), expand = c(0.04,0.04)) +

  labs(title = "G.",
       x = "Training condition",
       y = "Non-decision time") +
  theme(legend.position = "none",
        plot.title.position = "plot",
        plot.title = element_text(face = "bold"),
        axis.text = element_text(size = 12),
        axis.title = element_text(size = 13),
        plot.margin = margin(.5,.7,.7,.7, "cm"))

)

```

```{r}

## Bound

plot_bound <- with(param_ddm_test_exp2,aggregate(bound,by=list(condition,sub),mean))
names(plot_bound) <- c("cond","sub","bound")

plot_bound$cond <- factor(plot_bound$cond,levels=c("hard","average","easy"))
levels(plot_bound$cond)

plot_bound <-
  plot_bound %>%
  arrange(sub, cond)


# PLOT
(bound_exp2 <- ggplot(data=plot_bound, aes(y=bound, x=cond)) + 
  
  geom_line(aes(group=sub),size=.5,col="grey",alpha=.5,
             position = position_jitter(0.05, seed=2))+
  geom_point(size=2,col="grey",alpha=.6,
             position = position_jitter(0.05,seed=2)) +
  
  stat_summary(aes(group=1),geom = "line",fun = "mean",col = "black",size = 1.5) +
  stat_summary(geom = "point",fun = "mean",col = "black",size = 3) +
  stat_summary(fun.data = mean_se,geom = "errorbar",width=0,size=1) + 
    
  scale_y_continuous(expand = c(0.01,0.01)) +
  scale_x_discrete(labels=c("hard","average","easy"), expand = c(0.04,0.04)) +

  labs(title = "H.",
       x = "Training condition",
       y = "Bound") +
  theme(legend.position = "none",
        plot.title.position = "plot",
        plot.title = element_text(face = "bold"),
        axis.text = element_text(size = 12),
        plot.margin = margin(.5,.7,.7,.7, "cm"))

)

```

```{r}

## Drift interaction

plot_drift <- with(param_ddm_test_exp2,aggregate(drift,by=list(sub,condition,difflevel),mean))
names(plot_drift) <- c("sub","cond","trialdiff","drift")

plot_drift$cond <- factor(plot_drift$cond,levels=c("hard","average","easy"))
levels(plot_drift$cond)

plot_drift$trialdiff <- factor(plot_drift$trialdiff,levels=c("easy","average","hard"))
levels(plot_drift$trialdiff) <- c("Easy", "Average", "Hard")

plot_drift = summarySE(plot_drift, measurevar = "drift", 
                         groupvars = c("trialdiff", "cond"))

# PLOT
(drift_exp2 <- ggplot(data=plot_drift, aes(y=drift,x=cond,col=trialdiff)) + 
  
  geom_line(aes(group=trialdiff,linetype=trialdiff),size=1)+
  geom_point(size=2) +
  geom_errorbar(aes(ymin=drift-se, ymax=drift+se),width=0,size=.8) +
    
  scale_color_manual(values=c('orange', 'darkorange3','orangered4')) +

  scale_y_continuous(limits=c(0,.29),expand = c(0.01,0.01)) +
  scale_x_discrete(labels=c("Negative","Average","Positive"), expand = c(0.04,0.04)) +

  labs(title = "F.",
       x = "",
       y = "Drift rate",
       color= "Trial difficulty:",
       linetype= "Trial difficulty:") +
    
  theme(legend.position = c(.5,0.9),
        plot.title.position = "plot",legend.direction="horizontal",
        plot.title = element_text(face = "bold"),
        axis.text = element_text(size = 12),
        legend.title = element_text(size=10),
        plot.margin = margin(.7,.7,0,.7, "cm")) 
  #guides(color = guide_legend(title.position="top", title.hjust = 0.5))

)


```


```{r}

library(grid)
library(gridExtra)

jpeg(
  filename="ModelParameters_Exp2.jpeg",
  width=10,
  height=7,
  units="in",
  res=500)

lay <- rbind(c(1,2),
             c(3,4))

grid.arrange(vs_exp2,drift_exp2,ter_exp2,bound_exp2,
             layout_matrix=lay,
             top=textGrob("Exp. 2: Training difficulty",gp=gpar(fontsize=13,font=2)))


dev.off()


```



# Extra figures: effects per task

### Accuracy, exp 1 

```{r}

## Experiment 1
cor_sum = summarySE(Data1, measurevar = "cor", 
                         groupvars = c("trialdifflevel", "fbcond","task"))
cor_sum$task <- as.factor(cor_sum$task)
levels(cor_sum$task)

levels(cor_sum$task) <- c("Dot color","Dot number","Letter discrimination")

# PLOT
(acc_exp1 <- ggplot(data=cor_sum, 
             aes(y=cor, x=factor(trialdifflevel,level = c('hard','average','easy')),
                 color=factor(fbcond,level = c('lowSC','mediumSC','highSC')))) + 

  scale_color_manual(values = c(col_high,col_av,col_low),
                   labels=c('negative', 'average','positive')) +
  
  # Add behavioural Data
  geom_point(size=1) +
  geom_line(aes(group=fbcond),size=.6)+
  geom_errorbar(aes(ymin=cor-se, ymax=cor+se), width=.04) +
  
  facet_wrap(facets = vars(factor(task))) +
    
  scale_y_continuous(expand = c(0.01,0.01)) +
  scale_x_discrete(labels=c("hard","average","easy"), expand = c(0.04,0.04)) +

  labs(title = "B.",
       x = "",
       y = "Accuracy") +
  theme(legend.position = "",
        plot.title.position = "plot",
        plot.title = element_text(face = "bold"),        
        plot.margin = margin(.7,.7,0,.7, "cm"))
)


```

### RT, exp 1

```{r}

## Experiment 1
rt_sum = summarySE(Data1, measurevar = "rt", 
                         groupvars = c("trialdifflevel", "fbcond","task"))
rt_sum$task <- as.factor(rt_sum$task)
levels(rt_sum$task)

levels(rt_sum$task) <- c("Dot color","Dot number","Letter discrimination")


# PLOT
(rt_exp1 <- ggplot(data=rt_sum, 
             aes(y=rt, x=factor(trialdifflevel,level = c('hard','average','easy')),
                 color=factor(fbcond,level = c('lowSC','mediumSC','highSC')))) + 

  scale_color_manual(values = c(col_high,col_av,col_low),
                   labels=c('negative', 'average','positive')) +
  
  # Add behavioural Data
  geom_point(size=1) +
  geom_line(aes(group=fbcond),size=.6)+
  geom_errorbar(aes(ymin=rt-se, ymax=rt+se), width=.04) +
    
  facet_wrap(facets = vars(factor(task))) +

  scale_y_continuous(expand = c(0.01,0.01)) +
  scale_x_discrete(labels=c("hard","average","easy"), expand = c(0.04,0.04)) +

  labs(title = "C.",
       x = "",
       y = "RT (s)") +
  theme(legend.position = "",
        plot.title.position = "plot",
        plot.title = element_text(face = "bold"),        
        plot.margin = margin(.7,.7,0,.7, "cm"))
)

```


### Confidence data (main results)

```{r}

## Experiment 1
cj_sum = summarySE(Data1, measurevar = "cj", 
                         groupvars = c("trialdifflevel", "fbcond","task"))
cj_sum$task <- as.factor(cj_sum$task)
levels(cj_sum$task)

levels(cj_sum$task) <- c("Dot color","Dot number","Letter discrimination")


# PLOT
(cj_exp1 <- ggplot(data=cj_sum, 
             aes(y=cj, x=factor(trialdifflevel,level = c('hard','average','easy')),
                 color=factor(fbcond,level = c('lowSC','mediumSC','highSC')))) + 

  scale_color_manual(values = c(col_high,col_av,col_low),
                   labels=c('negative', 'average','positive')) +
  
  # Add behavioural Data
  geom_point(size=1) +
  geom_line(aes(group=fbcond),size=.6)+
  geom_errorbar(aes(ymin=cj-se, ymax=cj+se), width=.04) +
    
  facet_wrap(facets = vars(factor(task))) +

  scale_y_continuous(expand = c(0.01,0.01)) +
  scale_x_discrete(labels=c("hard","average","easy"), expand = c(0.04,0.04)) +

  labs(title = "A.",
       x = "",
       y = "Confidence",
       color="Exp. 1:\nComparative feedback") +
    
  theme(legend.position = "right",
        legend.title = element_text(face = "bold"),
        plot.title.position = "plot",
        plot.title = element_text(face = "bold"),        
        plot.margin = margin(.7,.7,0,.7, "cm")) 
)

```




### Accuracy, exp 2

```{r}

## Experiment 1
cor_sum = summarySE(Data2, measurevar = "cor", 
                         groupvars = c("trialdifflevel", "traindiffcond","task"))
cor_sum$task <- as.factor(cor_sum$task)
levels(cor_sum$task)

levels(cor_sum$task) <- c("Dot color","Dot number","Letter discrimination")

# PLOT
(acc_exp2 <- ggplot(data=cor_sum, 
             aes(y=cor, x=factor(trialdifflevel,level = c('hard','average','easy')),
                 color=factor(traindiffcond,level = c('hard','average','easy')))) + 

  scale_color_manual(values = c(col_high,col_av,col_low),
                  labels=c('hard', 'average','easy')) +
  
  # Add behavioural Data
  geom_point(size=1) +
  geom_line(aes(group=traindiffcond),size=.6)+
  geom_errorbar(aes(ymin=cor-se, ymax=cor+se), width=.04) +
  
  facet_wrap(facets = vars(factor(task))) +
    
  scale_y_continuous(expand = c(0.01,0.01)) +
  scale_x_discrete(labels=c("hard","average","easy"), expand = c(0.04,0.04)) +

  labs(title = "E.",
       x = "",
       y = "Accuracy") +
  theme(legend.position = "",
        plot.title.position = "plot",
        plot.title = element_text(face = "bold"),        
        plot.margin = margin(.7,.7,0,.7, "cm"))
)


```

### RT, exp 2

```{r}

## Experiment 1
rt_sum = summarySE(Data2, measurevar = "rt", 
                         groupvars = c("trialdifflevel", "traindiffcond","task"))
rt_sum$task <- as.factor(rt_sum$task)
levels(rt_sum$task)

levels(rt_sum$task) <- c("Dot color","Dot number","Letter discrimination")


# PLOT
(rt_exp2 <- ggplot(data=rt_sum, 
             aes(y=rt, x=factor(trialdifflevel,level = c('hard','average','easy')),
                 color=factor(traindiffcond,level = c('hard','average','easy')))) + 

  scale_color_manual(values = c(col_high,col_av,col_low),
                  labels=c('hard', 'average','easy')) +
  
  # Add behavioural Data
  geom_point(size=1) +
  geom_line(aes(group=traindiffcond),size=.6)+
  geom_errorbar(aes(ymin=rt-se, ymax=rt+se), width=.04) +
    
  facet_wrap(facets = vars(factor(task))) +

  scale_y_continuous(expand = c(0.01,0.01)) +
  scale_x_discrete(labels=c("hard","average","easy"), expand = c(0.04,0.04)) +

  labs(title = "F.",
       x = "",
       y = "RT (s)") +
  theme(legend.position = "",
        plot.title.position = "plot",
        plot.title = element_text(face = "bold"),        
        plot.margin = margin(.7,.7,0,.7, "cm"))
)

```


### Confidence data (main results)

```{r}

## Experiment 1
cj_sum = summarySE(Data2, measurevar = "cj", 
                         groupvars = c("trialdifflevel", "traindiffcond","task"))
cj_sum$task <- as.factor(cj_sum$task)
levels(cj_sum$task)

levels(cj_sum$task) <- c("Dot color","Dot number","Letter discrimination")


# PLOT
(cj_exp2 <- ggplot(data=cj_sum, 
             aes(y=cj, x=factor(trialdifflevel,level = c('hard','average','easy')),
                 color=factor(traindiffcond,level = c('hard','average','easy')))) + 

  scale_color_manual(values = c(col_high,col_av,col_low),
                  labels=c('hard', 'average','easy')) +
  
  # Add behavioural Data
  geom_point(size=1) +
  geom_line(aes(group=traindiffcond),size=.6)+
  geom_errorbar(aes(ymin=cj-se, ymax=cj+se), width=.04) +
    
  facet_wrap(facets = vars(factor(task))) +

  scale_y_continuous(expand = c(0.01,0.01)) +
  scale_x_discrete(labels=c("hard","average","easy"), expand = c(0.04,0.04)) +

  labs(title = "D.",
       x = "",
       y = "Confidence",
       color="Exp. 2:\nTraining difficulty") +
    
  theme(legend.position = "right",
        legend.title = element_text(face = "bold"),
        plot.title.position = "plot",
        plot.title = element_text(face = "bold"),        
        plot.margin = margin(.7,.7,0,.7, "cm")) 
)

```


```{r}

library(grid)
library(gridExtra)

jpeg(
  filename="Exra_EffectsPerTask.jpeg",
  width=12,
  height=12,
  units="in",
  res=500)

lay <- rbind(c(1,1),
             c(1,1),
             c(1,1),
             c(3,4),
             c(3,4),
             c(5,5),
             c(5,5),
             c(5,5),
             c(6,7),
             c(6,7))

grid.arrange(cj_exp1,
             acc_exp1,rt_exp1,
             cj_exp2,
             acc_exp2,rt_exp2,
             layout_matrix=lay)


dev.off()


```


# Quantitative fits figure

```{r}

setwd("Data/Aggregated")
quantData1 <- read.csv('quantitative_prediction_exp1.csv')
quantData2 <- read.csv('quantitative_prediction_exp2.csv')


## EXPERIMENT 1 --------------------

# Simulated data
cj_sim <-  aggregate(.~sub+trialdifflevel+condition,quantData1,mean)
cj_simsum = summarySE(cj_sim, measurevar = "cj", 
                         groupvars = c("trialdifflevel", "condition"))
cj_simsum$condition <- factor(cj_simsum$condition,levels=c("lowSC","mediumSC","highSC"))

# Behavioural data
cj_sum = summarySE(Data1, measurevar = "cj", 
                         groupvars = c("trialdifflevel", "fbcond"))
cj_sum$condition <- factor(cj_sum$fbcond, levels = c("lowSC","mediumSC","highSC"))



# PLOT
(cj_quant_exp1 <- ggplot(data=cj_simsum, 
             aes(y=cj, x=factor(trialdifflevel,level = c('hard','average','easy')),
                 color=condition)) + 
  
  scale_color_manual(values = c(col_low,col_av,col_high),
                    labels=c('negative', 'average','positive')) +
  scale_fill_manual(values = c(col_low,col_av,col_high),
                    labels=c('negative', 'average','positive')) +
  
  # Add Modelling Data
  geom_ribbon(aes(ymin=cj-se,ymax=cj+se,
                  group=condition,
                  fill=condition),
              colour="white",
              alpha=0.4) +


  # Behavioural data
  geom_line(data=cj_sum,size=1,
             aes(y=cj,
                 x=factor(trialdifflevel,level = c('hard','average','easy')),
                 group=condition)) +
  geom_point(data=cj_sum,size=2,
             aes(y=cj,
                 x=factor(trialdifflevel,level = c('hard','average','easy')),
                 shape=condition)) +
  geom_errorbar(data=cj_sum,
                aes(ymin=cj-se, ymax=cj+se), 
                width=0,size=1) +
    
    
  scale_y_continuous(limits = c(4,5.5),expand = c(0.01,0.01)) +
  scale_x_discrete(labels=c("hard","average","easy"), expand = c(0.03,0.03)) +

  labs(title = "Experiment 1: comparative feedback",
       y = "Confidence",
       x = "Trial difficulty") +
  theme(legend.position = "none",
        plot.title.position = "plot",
        plot.title = element_text(face = "bold"),
        axis.text = element_text(size = 12)) +
    
  guides(color = guide_legend(title.position="top", title.hjust = 0.5),
         fill = guide_legend(title.position="top", title.hjust = 0.5),
         shape = guide_legend(title.position="top", title.hjust = 0.5))

)




## EXPERIMENT 2 --------------------

# Simulated data
cj_sim <-  aggregate(.~sub+trialdifflevel+condition,quantData2,mean)
cj_simsum = summarySE(cj_sim, measurevar = "cj", 
                         groupvars = c("trialdifflevel", "condition"))
cj_simsum$condition <- factor(cj_simsum$condition,levels=c("hard","average","easy"))

# Behavioural data
cj_sum = summarySE(Data2, measurevar = "cj", 
                         groupvars = c("trialdifflevel", "traindiffcond"))
cj_sum$condition <- factor(cj_sum$traindiffcond, levels = c("hard","average","easy"))



# PLOT
(cj_quant_exp2 <- ggplot(data=cj_simsum, 
             aes(y=cj, x=factor(trialdifflevel,level = c('hard','average','easy')),
                 color=condition)) + 
  
  scale_color_manual(values = c(col_low,col_av,col_high),
                    labels=c('hard', 'average','easy')) +
  scale_fill_manual(values = c(col_low,col_av,col_high),
                    labels=c('hard', 'average','easy')) +
  
  # Add Modelling Data
  geom_ribbon(aes(ymin=cj-se,ymax=cj+se,
                  group=condition,
                  fill=condition),
              colour="white",
              alpha=0.4) +


  # Behavioural data
  geom_line(data=cj_sum,size=1,
             aes(y=cj,
                 x=factor(trialdifflevel,level = c('hard','average','easy')),
                 group=condition)) +
  geom_point(data=cj_sum,size=2,
             aes(y=cj,
                 x=factor(trialdifflevel,level = c('hard','average','easy')),
                 shape=condition)) +
  geom_errorbar(data=cj_sum,
                aes(ymin=cj-se, ymax=cj+se), 
                width=0,size=1) +
    
    
  scale_y_continuous(limits = c(4,5.5),expand = c(0.01,0.01)) +
  scale_x_discrete(labels=c("hard","average","easy"), expand = c(0.03,0.03)) +

  labs(title = "Experiment 2: Training difficulty",
       y = "",
       x = "Trial difficulty") +
  theme(legend.position = "none",
        plot.title.position = "plot",
        plot.title = element_text(face = "bold"),
        axis.text = element_text(size = 12)) +
    
  guides(color = guide_legend(title.position="top", title.hjust = 0.5),
         fill = guide_legend(title.position="top", title.hjust = 0.5),
         shape = guide_legend(title.position="top", title.hjust = 0.5))

)



## COMBINE -------------------

library(grid)
library(gridExtra)

setwd("C:/Users/u0140313/OneDrive - KU Leuven/Desktop/PriorBeliefs/Pierres_Files")


jpeg(
  filename="QuantitativeFits.jpeg",
  width=12,
  height=7,
  units="in",
  res=500)


grid.arrange(cj_quant_exp1,cj_quant_exp2,ncol=2)


dev.off()


```



